---
title: "ex_3_cornelius_mareis"
author: "Cornelius Mareis (12296117)"
date: "2023-06-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```


## Exercise 1

d)
Strengths: 
1. Being able to track your project in one sight and the possibility to revert to different stages of the project.
2. The fact that you can work with multiple people on a project.

Weaknesses:
1. Getting git started can be a very frustrating experience as it is very confusing without help.
2. The poor GUI of git and the fact that it isn't optimized for all operation systems e.g. Windows.

## Exercise 2

a)
repository link: git@github.com:c0oo/exeRcise-sheet-3.git

## Exercise 3

b)

```{r}
names_2021 <- read_csv("data/vornamen_2021.csv")
names_2022 <- read_csv("data/open_data_portal_2022.csv")

typeof(names_2021$Anzahl)
```

The count variable isn't numeric because the data is not complete as the count of uncommon names are only states as "4 or less" and because of that it cant be numeric.

```{r}
names_2021$Anzahl <- str_replace(names_2021$Anzahl, "4 oder weniger", "4")
names_2021$Anzahl <- as.numeric(names_2021$Anzahl)

names_2022$Anzahl <- str_replace(names_2022$Anzahl, "4 oder weniger", "4")
names_2022$Anzahl <- as.numeric(names_2022$Anzahl)
```

In my approach I just replaced all "4 oder weniger" with 4 and then changed it into numeric. The effect of this is, that the sum of the babies don't correspond to the reality but if we do it with both data sets we can at least compare them as all changes are the same.


c)

```{r}
sum(names_2021$Anzahl)
sum(names_2022$Anzahl)
```

The bigger baby-boom was in the year 2021.


d)

```{r}
names_2021 <- names_2021 %>% mutate(year = 2021)
names_2022 <- names_2022 %>% mutate(year = 2022)
```

e)

```{r}
combined_names <- bind_rows(names_2021, names_2022)
```

