---
title: "Exercise Sheet #3"
author: "Cornelius Mareis (12296117)"
date: "2023-06-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```


## Exercise 1

d)
Strengths: 
1. Being able to track your project in one sight and the possibility to revert to different stages of the project.
2. The fact that you can work with multiple people on a project.

Weaknesses:
1. Getting git started can be a very frustrating experience as it is very confusing without help.
2. The poor GUI of git and the fact that it isn't optimized for all operation systems e.g. Windows.

## Exercise 2

a)
repository link: 
git@github.com:c0oo/exeRcise-sheet-3.git
https://github.com/c0oo/exeRcise-sheet-3.git

## Exercise 3

b)

```{r}
names_2021 <- read_csv("data/vornamen_2021.csv")
names_2022 <- read_csv("data/open_data_portal_2022.csv")

typeof(names_2021$Anzahl)
```

The count variable isn't numeric because the data is not complete as the count of uncommon names are only states as "4 or less" and because of that it cant be numeric.

```{r}
names_2021$Anzahl <- str_replace(names_2021$Anzahl, "4 oder weniger", "4")
names_2021$Anzahl <- as.numeric(names_2021$Anzahl)

names_2022$Anzahl <- str_replace(names_2022$Anzahl, "4 oder weniger", "4")
names_2022$Anzahl <- as.numeric(names_2022$Anzahl)
```

In my approach I just replaced all "4 oder weniger" with 4 and then changed it into numeric. The effect of this is, that the sum of the babies don't correspond to the reality but if we do it with both data sets we can at least compare them as all changes are the same.


c)

```{r}
sum(names_2021$Anzahl)
sum(names_2022$Anzahl)
```

The bigger baby-boom was in the year 2021.


d)

```{r}
names_2021 <- names_2021 %>% mutate(year = 2021)
names_2022 <- names_2022 %>% mutate(year = 2022)
```

e)

```{r}
combined_names <- bind_rows(names_2021, names_2022)
```


f)

```{r}
table1 <- combined_names %>% group_by(Vorname) %>% summarise(Anzahl = sum(Anzahl)) %>% arrange(desc(Anzahl))  %>% head(10)
knitr::kable(table1, caption = "Top 10 baby names in the year 2021 and 2022 combined")
```


## Exercise 4

a)

The correct apply function for the column-wise means would be sapply(). 
lapply() didnt work because the second argument is "2" but should be a function or function name and "2" isn't a valid function. "mean" should have been the second argument.

prompt: 
1. the chunk of code
2. "can you tell me which apply function would be correct and why it didnt work?"

```{r}
# correct code

tax_data <- data.frame(
  Name = c("Munich GmbH", "ABC Inc.", "Backpacks 1980", "Bavarian Circus"),
  Tax_2019 = c(5000, 4000, 6000, 3500),
  Tax_2020 = c(4800, 4200, 5800, 3700),
  Tax_2021 = c(5200, 3800, 5900, 3400)
)

column_means <- sapply(tax_data[, -1], mean)
column_means

```

prompt:
(I didnt have to ask as ChatGPT automaticly corrected it in the last question)

```{r}
#rowwise means
tax_data <- data.frame(
  Name = c("Munich GmbH", "ABC Inc.", "Backpacks 1980", "Bavarian Circus"),
  Tax_2019 = c(5000, 4000, 6000, 3500),
  Tax_2020 = c(4800, 4200, 5800, 3700),
  Tax_2021 = c(5200, 3800, 5900, 3400)
)

row_means <- rowMeans(tax_data[, -1])
row_means

```

prompt:
Could you calculate the rowwise means?

b)

```{r}
# Define a nested list
nested_list <- list(
  a = 1,
  b = list(
    c = 2,
    d = list(
      e = 3,
      f = 4
    )
  ),
  g = 5
)

# Define a function to increment each element by 1
increment <- function(x) {
  x + 1
}

# Apply the increment function using rapply
result <- rapply(nested_list, increment)

# Print the result
print(result)

```

The rapply() function is used to recursively apply a function to elements of a nested lists for example. In this example rapply() adds the increment recursively to each element in the nested list. The resulting list contains the incremented values. 

prompt:
can you explain what the rapply() function does and give an easy example with mock data where the function is used?